ECE 612, Information Theory

### 2024-04-09 information-theory/main.tex
Checkpoint

    Where $P$ is the power constraint, and $\sigma^2$ is the variance of the Gaussian noise. The maximum is achieved when $X$ follows Gaussian distribution $X \leftsample N(0, P)$
\end{theorem}

>>>>

    Where $P$ is the power constraint, and $\sigma^2$ is the variance of the Gaussian noise. The maximum is achieved when $X$ follows Gaussian distribution $X \sim N(0, P)$
\end{theorem}

\subsection{Parallel Gaussian Channel}
Suppose for $1 \leq l \leq n$, $Y_l = X_l + Z_l$, where $Z_l \sim N(0, N_l)$ is independent Gaussian noise, then $\mathbf{Y} = (Y_l)_{l=1}^n$ can be seen as the output of $n$ parallel Gaussian channels combined into a single channel. The capacity of the combined channel is

\begin{equation*}
    C = \max_{f_\mathbf{X}}I(\mathbf{X}; \mathbf{Y})
\end{equation*}

The optimal strategy for maximizing the capacity is to make $X_l$ independent and individually Gaussian. If there is a combined power constraint $\sum_{l=1}^nE[X_l^2] \leq P$, then \textit{power should be first given to the channel with the lowest amount of noise until the combined noise + power exceeds the next lowest noise} (\textbf{waterfilling}).
